Efficient pedigree recording for fast population genetics simulation

### 2018-01-06 forwards_paper.tex
added points to the abstract, re: #47

\begin{abstract}
    In this paper we describe how to
    efficiently record the entire genetic history of a population
    during a forwards-time, individual-based population genetics simulation.
    This allows us to dramatically reduce the computational burden of tracking individual genomes
    by simulating only those loci that may affect reproduction (those having non-neutral variants),
    and recording history in the \emph{tree sequence} format introduced in the software package \msprime,
    on which neutral mutations can be quickly placed afterwards.
    We implement the method in two popular forwards-time simulation frameworks,
    and show that not only does this speed up large simulations by one or two orders of magnitude,
    but saves not only full genotype sequences, but also all marginal
    geneologies of the simulated individuals.
    % This has the promise of making large-scale, whole-genome simulations with realistic geography and selection finally possible.
\end{abstract}

>>>>

\begin{abstract}
    In this paper we describe how to
    efficiently record the entire genetic history of a population
    during a forwards-time, individual-based population genetics simulation.
    This allows us to dramatically reduce the computational burden of tracking individual genomes
    by simulating only those loci that may affect reproduction (those having non-neutral variants),
    and recording history in the \emph{tree sequence} format introduced in the software package \msprime,
    on which neutral mutations can be quickly placed afterwards.
    We implement the method in two popular forwards-time simulation frameworks,
    which speeds up large, whole-genome simulations by one or two orders of magnitude.
    In addition to speed, we show that the method has several advantages:
    (1) All marginal genealogies of the simulated individuals are recorded, rather than just genotypes.
    (2) A population of $N$ individuals with $M$ polymorphic sites
    can be stored on $O(N \log N + M)$ space, making it feasible to store a simulation's entire final generation
    rather than only a subset.
    (3) A simulation can easily be initialized with prior history produced by a more efficient coalescent simulation of deep history.
    To make these possible, 
    we introduce the \msprime{} Tables API, which allows for the efficient interchange of genealogical data between modular program components.
\end{abstract}
